Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-01-20 paper/main.tex
* reduce spacing even more.
fix smaller -> larger in uborda

%% Revision documents
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}
% FIXME: \sout is not very good. It cannot handle commands within its argument.
\newcommand{\SuggestEdit}[3][red]{\textcolor{#1}{\sout{#2}}\textcolor{#1}{#3}}
\let\svthefootnote\thefootnote
\newcommand\colorfootnote[2][black]{\def\thefootnote{\color{#1}\svthefootnote}%
  \footnote{\color{#1}#2}\def\thefootnote{\color{black}\svthefootnote}}
\newcommand\RevComment[3][red]{\protect\colorfootnote[#1]{{\textbf{[#2: #3]}}}}
% Command for edits, command for commenting and color
\newcommand\newrevisor[3]{%%
  \colorlet{#1}{#3}
  \expandafter\newcommand\csname#1\endcsname[2]{\SuggestEdit[#1]{##1}{##2}}%%
  \expandafter\newcommand\csname#2\endcsname[1]{\RevComment[#1]{#2}{##1}}%%
}
\newrevisor{manuel}{MANUEL}{Purple}
\newrevisor{ekhine}{EKHINE}{red}

@@

Borda and uBorda are equivalent when $w(\sigma)$ is constant for every $\sigma$. Otherwise, uBorda ranking will be closer to the rankings in $S$ with smaller value of $w(\sigma)$. Roughly speaking, it is equivalent to replicating in the sample the $\sigma$ with low values of $w(\sigma$).
The choice of  $w(\sigma)$ depends on the relevant property of a ranking in a particular domain.
%% MANUEL: To save space.
%For example, uBorda has been shown to have nice theoretical properties for the online estimation of the parameters of a sample with concept drift~\cite{IruLobPer2020arxiv}.
%
% In this paper, we would like to replicate each permutation $\sigma$ a number of times that is inversely proportional to $f(\sigma)$. Therefore, we will use $w(\sigma)=\rho^{f(\sigma)}$ for a $\rho\in(0,1)$.
Finally, uBorda is computed in polynomial time.

@@

%: LOP reales: he puesto 3 de diferentes tamanos. Me ha parecido interesante que, a pesar de que CEGO parece que va mejor, esta diferencia se va reduciendo segun se aumenta el tamano del problema (que se puede ver en el nombre del problema y en el títutlo de la gráfica)
\begin{figure}[!tbp]
  \centering%
  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandB_N-p50-01}\\
  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d100_01}\\
  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d150_01}\\
%  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d200_01}\\
    \caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on three instances from LOLIB.\label{fig:lolib}}
  \end{figure}

>>>>

%% Revision documents
\usepackage[dvipsnames]{xcolor}
\usepackage[normalem]{ulem}
% FIXME: \sout is not very good. It cannot handle commands within its argument.
\newcommand{\SuggestEdit}[3][red]{\textcolor{#1}{\sout{#2}}\textcolor{#1}{#3}}
\let\svthefootnote\thefootnote
\newcommand\colorfootnote[2][black]{\def\thefootnote{\color{#1}\svthefootnote}%
  \footnote{\color{#1}#2}\def\thefootnote{\color{black}\svthefootnote}}
\newcommand\RevComment[3][red]{\protect\colorfootnote[#1]{{\textbf{[#2: #3]}}}}
% Command for edits, command for commenting and color
\newcommand\newrevisor[3]{%%
  \colorlet{#1}{#3}
  \expandafter\newcommand\csname#1\endcsname[2]{\SuggestEdit[#1]{##1}{##2}}%%
  \expandafter\newcommand\csname#2\endcsname[1]{\RevComment[#1]{#2}{##1}}%%
}
\newrevisor{manuel}{MANUEL}{Purple}
\newrevisor{ekhine}{EKHINE}{red}
%\usepackage{showframe}

@@

Borda and uBorda are equivalent when $w(\sigma)$ is constant for every $\sigma$. Otherwise, uBorda ranking will be closer to the rankings in $S$ with larger value of $w(\sigma)$. Roughly speaking, it is equivalent to replicating in the sample the $\sigma$ with high values of $w(\sigma$).
The choice of  $w(\sigma)$ depends on the relevant property of a ranking in a particular domain.
%% MANUEL: To save space.
%For example, uBorda has been shown to have nice theoretical properties for the online estimation of the parameters of a sample with concept drift~\cite{IruLobPer2020arxiv}.
%
% In this paper, we would like to replicate each permutation $\sigma$ a number of times that is inversely proportional to $f(\sigma)$. Therefore, we will use $w(\sigma)=\rho^{f(\sigma)}$ for a $\rho\in(0,1)$.
Finally, uBorda is computed in polynomial time.

@@

%: LOP reales: he puesto 3 de diferentes tamanos. Me ha parecido interesante que, a pesar de que CEGO parece que va mejor, esta diferencia se va reduciendo segun se aumenta el tamano del problema (que se puede ver en el nombre del problema y en el títutlo de la gráfica)
\begin{figure}[!tb]
  \centering%
  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandB_N-p50-01}\\
  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d100_01}\\
  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d150_01}\\
%  \includegraphics[width=\textwidth]{../img/fitness_real_lop_RandA1_N-t1d200_01}\\
    \caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on three instances from LOLIB.\label{fig:lolib}}
  \end{figure}
